---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `targets` package minimal example

[![Launch RStudio Cloud](https://img.shields.io/badge/RStudio-Cloud-blue)](https://rstudio.cloud/project/1430691)

This repository is an example data analysis workflow with [`targets`](https://docs.ropensci.org/targets). The pipeline reads the data from a file, preprocesses it, visualizes it, and fits a regression model. 

## How to access

You can try out this example project as long as you have a browser and an internet connection. [Click here](https://rstudio.cloud/project/1430691) to navigate your browser to an RStudio Cloud instance. Alternatively, you can clone or download this code repository and install the R packages [listed here](https://github.com/wlandau/targets-minimal/blob/03835c2aa4679dcf3f28c623a06d7505b18bee17/DESCRIPTION#L25-L30).

## How to run

In the R console, call the [`tar_make()`](https://wlandau.github.io/targets/reference/tar_make.html) function to run the pipeline. Then, call `tar_read(hist)` to retrieve the histogram. Experiment with [other functions](https://wlandau.github.io/targets/reference/index.html) such as [`tar_visnetwork()`](https://wlandau.github.io/targets/reference/tar_visnetwork.html) to learn how they work.

## File structure

The most important files are:

```{r, eval = FALSE}
├── _targets.R
├── R/
├──── functions.R
├── data/
├──── raw_data.csv
└── index.Rmd
```

File | Purpose
---|---
[`_targets.R`](https://github.com/wlandau/targets-minimal/blob/main/_targets.R) | The special R script that declares the [`targets`](https://docs.ropensci.org/targets) pipeline. See `tar_script()` for details.
[`R/functions.R`](https://github.com/wlandau/targets-minimal/blob/main/R/functions.R) | An R script with user-defined functions. Unlike [`_targets.R`](https://github.com/wlandau/targets-minimal/blob/main/_targets.R), there is nothing special about the name or location of this script. In fact, for larger projects, it is good practice to partition functions into multiple files.
[`data/raw_data.csv`](https://github.com/wlandau/targets-minimal/blob/main/data/raw_data.csv) | The raw `airquality` dataset.
[`index.Rmd`](https://github.com/wlandau/targets-minimal/blob/main/index.Rmd): an R Markdown report that reruns in the pipeline whenever the histogram of ozone changes ([details](https://books.ropensci.org/targets/files.html#literate-programming)).

## Continuous deployment

Whenever this GitHub repository is updated, the `targets` pipeline runs in a [GitHub Actions workflow](https://github.com/wlandau/targets-minimal/actions). The workflow pushes the results to the [`targets-runs`](https://github.com/wlandau/targets-minimal/tree/targets-runs) branch, and the R Markdown report is deployed to <https://wlandau.github.io/targets-minimal/> using [GitHub Pages](https://pages.github.com/). Subsequent runs restore the output files from the previous run so up-to-date targets do not rebuild. To enable continuous deployment in your own project:

1. Set up your project with [`renv`](https://rstudio.github.io/renv/).
    * Call `targets::tar_renv()` to write a `_packages.R` file to expose hidden dependencies.
    * Call `renv::init()` to initialize the package library.
    * At minimum, commit files `.Rprofile`, `renv.lock`, and `renv/activate.R` to your Git repository.
2. Commit the [`.github/workflows/targets.yaml`](https://github.com/wlandau/targets-minimal/blob/main/.github/workflows/targets.yaml) workflow file to your Git repository.
3. Ensure GitHub Actions are enabled in the Settings tab of your GitHub repository's website.
4. GitHub has strict storage and compute limitations, so this pattern is only appropriate for small [`targets`](https://docs.ropensci.org/targets) pipelines. Before you push, ensure your resource requirements are minimal. For storage, you may choose the AWS-backed storage formats (e.g. `tar_target(..., format = "aws_qs")`) to reduce the burden.

