---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `targets` package minimal example

[![Launch RStudio Cloud](https://img.shields.io/badge/RStudio-Cloud-blue)](https://rstudio.cloud/project/1430691)

This repository is an example data analysis workflow with [`targets`](https://github.com/wlandau/targets). The pipeline reads the data from a file, preprocesses it, visualizes it, and fits a regression model. 

## How to access

You can try out this example project as long as you have a browser and an internet connection. [Click here](https://rstudio.cloud/project/1430691) to navigate your browser to an RStudio Cloud instance. Alternatively, you can clone or download this code repository and install the R packages [listed here](https://github.com/wlandau/targets-minimal/blob/03835c2aa4679dcf3f28c623a06d7505b18bee17/DESCRIPTION#L25-L30).

## How to run

In the R console, call the [`tar_make()`](https://wlandau.github.io/targets/reference/tar_make.html) function to run the pipeline. Then, call `tar_read(hist)` to retrieve the histogram. Experiment with [other functions](https://wlandau.github.io/targets/reference/index.html) such as [`tar_visnetwork()`](https://wlandau.github.io/targets/reference/tar_visnetwork.html) to learn how they work.

## File structure

The files in this example are organized as follows.

```{r, eval = FALSE}
├── _targets.R
├── R/
├──── functions.R
├── data/
├──── raw_data.csv
└── index.Rmd
```

File | Purpose
---|---
[`_targets.R`](https://github.com/wlandau/targets-minimal/blob/main/_targets.R) | The special R script that declares the [`targets`](https://github.com/wlandau/targets) pipeline. See `tar_script()` for details.
[`R/functions.R`](https://github.com/wlandau/targets-minimal/blob/main/R/functions.R) | An R script with user-defined functions. Unlike [`_targets.R`](https://github.com/wlandau/targets-minimal/blob/main/_targets.R), there is nothing special about the name or location of this script. In fact, for larger projects, it is good practice to partition functions into multiple files.
[`data/raw_data.csv`](https://github.com/wlandau/targets-minimal/blob/main/data/raw_data.csv) | The raw `airquality` dataset.
[`index.Rmd`](https://github.com/wlandau/targets-minimal/blob/main/index.Rmd): an R Markdown report that reruns in the pipeline whenever the histogram of ozone changes ([details](https://books.ropensci.org/targets/files.html#literate-programming)).

## Continuous deployment

This pipeline runs in a [GitHub Actions workflow](https://github.com/wlandau/targets-minimal/actions) on every push to the main branch. The [cache action](https://github.com/actions/cache) restores the latest `_targets/` data store and rendered `index.html` file before each run so that up-to-date targets do not rebuild. The latest run is committed and pushed to the [`latest-run`](https://github.com/wlandau/targets-minimal/tree/latest-run) branch, and the R Markdown report is deployed to <https://wlandau.github.io/targets-minimal/> using [GitHub Pages](https://pages.github.com/). To activate similar continuous deployment in your own projects, simply copy [`.github/workflows/targets.yaml`](https://github.com/wlandau/targets-minimal/blob/main/.github/workflows/targets.yaml) to your own repo. Please read about the [storage limitations described here](https://docs.github.com/en/actions/guides/caching-dependencies-to-speed-up-workflows#usage-limits-and-eviction-policy).
