---
title: "Validation results"
author: "You"
date: "6/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet = TRUE)
```

This report contains the validation results of a small Bayesian hierarchical model. Here, we summarize the results computed in earlier targets of the pipeline. We reference our targets with `tar_load()` and `tar_read()`. This ensures

1. Because of the `tar_knitr()` call (see `_targets.R`) `targets` automatically detects the dependencies of this report and rebuilds it when its dependencies change.
1. We can run the report by itself if the targets are already in the `_targets/` data store.

```{r}
library(targets)
tar_load(fit)
```

Our results are in a data frame with one row per simulated dataset and the following columns.

* `cover_beta`: Logical, whether the true value of `beta`
  is covered in the 50% credible interval from the model.
* `beta_true`: True value of `beta` used to simulate the original data.
* `beta_25`: posterior 25th percentile of `beta`.
* `beta_median`: posterior median of `beta`.
* `beta_75`: posterior 75th percentile of `beta`.
* `psrf`: Maximum potential scale reduction factor across all the model parameters. A value above 1.1 is traditionally considered evidence of lack of convergence.
* `ess`: Minimum effective sample size across all the model parameters. If this value is far lower than the number of non-warmup MCMC iterations, this is evidence of MCMC autocorrelation, which could mean the model needs reparameterization.

```{r, paged.print = FALSE}
fit
```

If we implemented the model in `stan/model.stan` correctly, then roughly 50% of model fits should cover the true `beta` parameter that generated the data.

```{r}
mean(fit$beta_cover)
```

The posterior median of `beta` should be reasonably close to the true value.

```{r}
ggplot(fit) +
  geom_point(aes(x = beta_true, y = beta_median)) +
  geom_abline(intercept = 0, slope = 1) +
  theme_gray(16)
```

We should also check convergence diagnostics. `psrf` should ideally be low.

```{r}
ggplot(fit) +
  geom_histogram(aes(x = psrf))
```

Effective sample size should ideally be high.

```{r}
ggplot(fit) +
  geom_histogram(aes(x = ess))
```

